\documentclass[letterpaper,11pt]{article}
\usepackage{fancyhdr}

\setlength{\footskip}{5pt}

\usepackage{latexsym}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeProjectHeadingTwoLine}[3]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \textit{\small #3} \\
      \small\emph{#2} & \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://aadityabhatia.com/}{\Large Aaditya Bhatia}} & Email: \href{mailto:aaditya.tec@gmail.com}{aaditya.tec@gmail.com} \\
  \href{https://www.linkedin.com/in/aaditya-bhatia/}{Linkedin} & Mobile: +91 9999697291 \\
  \href{https://github.com/aadi121205}{Github} & \href{https://aadityabhatia.com/}{aadityabhatia.com} \\
\end{tabular*}

\section{Experience}

  \resumeSubHeadingListStart

\resumeSubheading
{Summer Technology Analyst Intern}{May 2026 -- Present}
{Morgan Stanley}{Mumbai, IN}
\resumeItemListStart

  \resumeItem{Contributed to the modernization of a legacy internal platform, refactoring core modules onto a modern service-based stack and cutting manual developer workflows by \textbf{30\%+}.}

  \resumeItem{Integrated \textbf{5+ MCP (Model Context Protocol) servers} and \textbf{multiple LLM/model APIs} into an internal AI chatbot, expanding it from a simple Q\&A assistant into an agentic system capable of multi-step tool use.}

  \resumeItem{Built agentic integrations connecting the chatbot to internal tools and data sources, automating retrieval and actioning across \textbf{multiple internal systems} and reducing common lookup tasks from minutes to seconds.}

\resumeItemListEnd

\resumeSubheading
{Software Head}{Sept 2023 -- Present}
{UAS-DTU}{Delhi, IN}
\resumeItemListStart

  \resumeItem{Spearheaded the complete lifecycle design, development, and optimization of \textbf{3+ advanced computer vision pipelines}—including Semantic Segmentation, ODLC, and Remote Physiological Signature Estimation—utilizing CNNs and autoencoders, improving detection and classification accuracy by \textbf{20\%+}.}
  \resumeItem{Architected and deployed a robust full-stack web application leveraging Flask, React, DroneKit (Python), Socket.IO, and Docker for real-time image analytics and telemetry visualization, used across \textbf{2 international competitions} and \textbf{5+ field deployments}.}
\resumeItem{Pioneered research and implementation of state-of-the-art vision architectures, including ViTs, CLIP-based zero-shot models, and advanced CNN backbones, to support rapid medical triage within the \textbf{DARPA Triage Challenge (\$210K in prizes won)}. Integrated reinforcement learning-driven decision modules and multi-modal perception pipelines for casualty prioritization, context-aware scene understanding, and remote patient monitoring under real-world operational constraints.}

\resumeItemListEnd

\resumeSubheading
{Research Intern in Wirocomm Lab}{Jun 2025 -- Oct 2025}
{Indraprastha Institute of Information Technology, Delhi}{Delhi, IN}
\resumeItemListStart

  \resumeItem{Developed a Deep Q-Learning agent to optimize traffic signal control using SUMO simulations, reducing average vehicle wait times by \textbf{25\%+} over fixed-time baselines through deep reinforcement learning.}

  \resumeItem{Implemented neural networks with Keras integrated with SUMO via TraCI, training agents across \textbf{1,000+ simulated episodes} of realistic urban traffic scenarios.}

\resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Achievements}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{DARPA Triage Challenge (Systems)}}{2024}
\resumeItemListStart
  \resumeItem{Secured \textbf{2nd place in Phase 1} (\$60,000) and \textbf{2nd place in Phase 2} (\$150,000) in the DARPA Triage Challenge (Hosted By US DOD)(Non-Funded Category) as a core contributor to UAS-DTU. Outperformed multiple university and industry teams across perception, autonomy, and triage decision-making benchmarks.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{International Conference on Unmanned Aerial Systems (ICUAS) 2024}}{2024}
\resumeItemListStart
  \resumeItem{Achieved \textbf{2nd place} in the indoor simulation phase and \textbf{3rd place overall} in the ICUAS 2024 competition as part of team UAS-DTU.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Smart India Hackathon}}{2022}
\resumeItemListStart
  \resumeItem{Winner in the \textbf{Drones and Robotics} Jr category, leading Team Falken.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeadingTwoLine
{DARPA Triage Challenge — Real-Time GCS \& GUI Platform}
{React, TypeScript, Flask, Socket.IO, Docker, Linux}
{Jan 2024 -- Present}
\resumeItemListStart
  \resumeItem{Designed and implemented a scalable, real-time Ground Control System (GCS) for autonomous medical triage missions, enabling monitoring and control of \textbf{5+ heterogeneous UAV/UGV subsystems} from a single operator station.}
  \resumeItem{Built a React + TypeScript frontend streaming \textbf{10+ concurrent} live telemetry, image, and casualty-state feeds into mission-level decision dashboards.}
  \resumeItem{Architected a Flask + Socket.IO backend delivering \textbf{sub-second} communication between perception pipelines, autonomy modules, and distributed edge devices.}
  \resumeItem{Containerized the full-stack system using Docker and deployed across high-performance Linux servers and edge platforms including Nvidia Jetson Orin NX.}
\resumeItemListEnd

\resumeProjectHeadingTwoLine
{DARPA Triage Challenge — Reinforcement Learning–Based Triage Decision System}
{Python, PyTorch, Reinforcement Learning, Multi-Modal AI}
{Jan 2024 -- Present}
\resumeItemListStart
  \resumeItem{Developed reinforcement learning–driven decision modules for autonomous casualty prioritization under uncertain, partially observable disaster environments.}
  \resumeItem{Integrated \textbf{3 modalities} of perception input—vision-based injury detection (CLIP, ViTs, CNNs), physiological signal estimates, and scene context—into RL state representations.}
  \resumeItem{Designed reward functions to balance survival probability, response time, and limited resource allocation constraints.}
  \resumeItem{Evaluated policies in simulated and real-world mission scenarios to enable context-aware triage recommendations with minimal human intervention.}
\resumeItemListEnd

\resumeProjectHeadingTwoLine
{ICUAS 2024 — Autonomous Indoor Drone Navigation}
{Python, ROS 2, Docker, NumPy, PyTorch}
{Feb 2024 -- Sept 2024}
\resumeItemListStart
  \resumeItem{Developed a ROS 2-based autonomous navigation stack for indoor UAVs with real-time perception, localization, and control.}
  \resumeItem{Implemented object detection and collision avoidance pipelines using NumPy and PyTorch.}
  \resumeItem{Containerized the complete simulation and development environment using Docker for reproducible builds and rapid deployment.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL (Postgres), Java/TypeScript, HTML/CSS, Bash, Fish, \LaTeX} \\
     \textbf{Frameworks}{: React, Node.js, Flask, FastAPI, ROS 2, CUDA, Material-UI, Socket.IO, DroneKit} \\
     \textbf{AI/LLM}{: MCP (Model Context Protocol), LLM/Model APIs (Anthropic, OpenAI), Agentic Systems, Reinforcement Learning} \\
     \textbf{Developer Tools}{: Git, Docker, Podman, GitHub Actions, TravisCI, Google Cloud Platform, VS Code, JetPack, Ubuntu/Debian, Arch Linux} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, PyTorch, TensorFlow, Keras, OpenCV, SUMO/TraCI} \\
     \textbf{Hardware}{: NVIDIA Jetson Nano, NVIDIA Jetson Orin, Raspberry Pi, Intel Realsense Tracking Cameras, LiDARs, Pixhawk Cube Orange/Black} }}
 \end{itemize}

\section{Education}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Technological University}{Delhi, IN}
      {Bachelor of Technology in Computer Science Engineering}{Aug 2023 -- May 2027}
    \resumeSubheading
      {The Heritage School}{Delhi, IN}
      {High School Diploma in Science and Computer Science}{April 2019 -- April 2023}
  \resumeSubHeadingListEnd

\end{document}

